Social_Isolation_and_Loneliness

### 2023-03-04 FEM_R/Loneliness_Social_Isolation/PAPER_WORKING_SCRIPT.Rmd
Updated the settings.csv and .txt files with the new vars for the loneliness and social isolation scenario runs. Also wrote a utilities function in R for collating detailed output files, and some more variable checking in the R working scripts. Also imputed some things in kludge.do, and need to investigate why lnly values are not being imputed properly
Added a title to a section in Rmd

```{r}
## Directories
base_output_dir <- "output/LNLY_SOCISO/"
input_dir <- "input_data/"

@@

```{r}
diseaseFreeLifeYearsComp(cohort_full, no.lonely, 'No Loneliness')
diseaseFreeLifeYearsComp(cohort_full, no.sociso, 'No Social Isolation')
diseaseFreeLifeYearsComp(cohort_full, no.lnly.sociso, 'No Loneliness OR Social Isolation')
```

>>>>

```{r}
## Directories
base_output_dir <- "output/LNLY_SOCISO_TEST/"
input_dir <- "input_data/"

@@

#### Disease Free Life Years
```{r}
diseaseFreeLifeYearsComp(cohort_full, no.lonely, 'No Loneliness')
diseaseFreeLifeYearsComp(cohort_full, no.sociso, 'No Social Isolation')
diseaseFreeLifeYearsComp(cohort_full, no.lnly.sociso, 'No Loneliness OR Social Isolation')
```

```{r}
